---
title: "Optimization Homework 2"
author: "Rebecca Wood"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

#Matrix Representation
```{r, echo=FALSE, include=FALSE}
library(optrees)
library(igraph)
```

```{r, echo=TRUE, warning=FALSE}
n <- 1000
d <- runif(n*n)
d[d < 0.8] <- NA
d <- matrix(d, nrow = n)
diag(d) <- NA
d[upper.tri(d)] = t(d)[upper.tri(d)]

AdjMatrix2List <- function(d) {
  count = 0
  for(i in 1:nrow(d)){
    for(j in 1:ncol(d)){
      if(!is.na(d[i,j])){
        count = count + 1
      }
    }
  }

  ds <- matrix(NA, nrow = count, ncol = 3)
  colnames(ds) <- c("head", "tail", "weight")
  k = 0
  for(i in 1:nrow(d)){
    for(j in 1:ncol(d)){
      if(!is.na(d[i,j])){
        k = k +1
        ds[k,1] = i
        ds[k,2] = j
        ds[k,3] = d[i,j]
      }
    }
  }
  return(ds)
}

ds <- AdjMatrix2List(d)

str(ds)
head(ds)
```

***

#Euclidean Minimum Spanning Tree

```{r, echo=TRUE, warning=FALSE}
n <- 50
x <- round(runif(n)*1000)
y <- round(runif(n)*1000)
plot(x,y, pch=16)

num <- rep(0,2500)
d <- matrix(num, length(x), length(y))

for(i in 1:n){
  for(j in 1:n){
    d[i,j] = sqrt((x[i] - x[j])**2 + (y[i] - y[j])**2)
  }
}

ds <- AdjMatrix2List(d)


ds.mst <- msTreeKruskal(1:n, ds)
str(ds.mst)
```
```{r, echo=TRUE}
plot.mst <- function(arclist){
  segments(x[arclist[,1]], y[arclist[,1]], x[arclist[,2]], y[arclist[,2]])
}

plot(x,y,pch=16)
plot.mst(ds.mst$tree.arcs)
```

***  

#Hostile Agents

So we have that there are $n$ agents in a hostile area. Between any two agents, $i$ and $j$, a message at the probability $p_{i_j}$ of being intercepted by the hostile community. We want to determine the best method for sending a single message to all agents with the lowest probability of being intercepted by hostile hands.

1. We want to transmit a message to ALL agents within this hostile area. The probability (which cannot be negative), needs to be minimized. Thus, we can assume we have a directed, acyclic graph - DAG. Each agent must be a node, the message moves from one agent to the next, and it would be safe to assume that once the message is received by an agent that agent will not receive the message again (that would cause a cycle, otherwise). Thus, we must solve a DAG.

2. The inputs of this graph would be the agents, while the edge weights would correspond to the probability of the message being intercepted by hostile hands.

3. Due to the problem creating a DAG, we can solve this solving the minimum spanning tree; therefore, Kruskal's Algorithm. We want to hit every node, once, while maintaining the lowest probability of being intercepted by hostile hands.

4. The computational efficiency of this solution would be $O(n \ lg \ n)$.

***

#5 Project Scheduling

##1693 Analysis
The following sections of code are slightly out of order. Close to the end of this section, Section 5.4: Final Table, gives the calculated values in a table, as well as the overall earliest completion time and date.

###5.4 Early Start Time
```{r, echo=TRUE, warning=FALSE}
library(gridExtra)
library(grid)
library(igraph)
s.labels <- c('a','b', 'c', 'd', 'e', 'f', 'g', 'h', 'i', 'j')
s.nodes <- c(90, 15, 5, 20, 21, 25, 14, 28, 30, 45)
s.head <- c('a', 'b', 'g', 'd', 'a', 'c', 'f', 'd', 'a', 'd', 'i')
s.esheadnum <- c(1, 2, 7, 4, 1, 3, 6, 4, 1, 4, 9) ##
s.tail <- c('b', 'c', 'd', 'e', 'f', 'g', 'g', 'h', 'i', 'j', 'j')
s.estailnum <- c(2, 3, 4, 5, 6, 7, 7, 8, 9, 10, 10) ##
s.esweight <- -c(90, 15, 14, 20, 90, 5, 25, 20, 90, 20, 30) ##

s.esmatrix <- cbind(s.esheadnum, s.estailnum, s.esweight)
#grid.table(s.matrix)

esshortpath <- getShortestPathTree(1:10, s.esmatrix, algorithm = "Bellman-Ford",
  directed = TRUE, show.data = TRUE, show.graph = TRUE, show.distances = TRUE)

es <- -esshortpath$distances
```

###5.7 Late Finish Time
```{r, echo=TRUE}
lfhead <- c(2, 3, 4, 5, 6, 7, 7, 8, 9, 10, 10,11,11,11)
lftail <- c(1, 2, 7, 4, 1, 3, 6, 4, 1, 4, 9,5,8,10)
lfweight <- -c(15,5,20,21,25,14,14,28,30,45,45,0,0,0)
lfmatrix <- cbind(lfhead, lftail, lfweight)

lfsp <- getShortestPathTree(1:11, lfmatrix, algorithm = "Bellman-Ford",
    source.node = 11, directed=TRUE)
```
```{r,echo = TRUE}
lf <- lfsp$distances[-11]+194
```
###5.6 Early Finish Time
```{r, echo=TRUE}
s.efheadnum <- c(1, 2, 7, 4, 1, 3, 6, 4, 1, 4, 9)
s.eftailnum <- c(2, 3, 4, 5, 6, 7, 7, 8, 9, 10, 10)
ef <- es + s.nodes
```

###5.8 Late Start Time

```{r, echo=TRUE}
ls <- lf - s.nodes
```

###5.9 Slack
```{r, echo=TRUE}
slack <-lf - ef
```
###5.5 Final Table
```{r, echo=TRUE}
task <- s.labels
duration <- s.nodes
finaltimes <- data.frame(task, duration, es, ls, ef, lf, slack)
grid.table(finaltimes)
```
Based on this table, the earliest completion time will happen at day 194. Assuming we start the tasks on November 1, 2017, this would give a completion date of May 14, 2018.

***

##Gantt Chart (Extra)

```{r, echo=TRUE, fig.height=4, fig.width=7}
desc <- c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J")
barplot(rbind(lf-duration, duration), horiz=TRUE, col=c("white","gray"),
        border = 0, names.arg = desc, las = 1)
```